Reproducibility in Plant Pathology

### 2018-05-22 README.rmd
Update README.rmd/md and release for DOI

---
title: "Reproducibility in Plant Pathology"
output: github_document
---

[![Travis-CI Build Status](https://travis-ci.org/openplantpathology/Reproducibility_in_Plant_Pathology.svg?branch=master)](https://travis-ci.org/openplantpathology/Reproducibility_in_Plant_Pathology)

## A research compendium for a report on the reproducibility of research in plant pathology

For optimal webviewing of this report, please see the
[HTML version](http://htmlpreview.github.io/?https://github.com/openplantpathology/Reproducibility_in_Plant_Pathology/blob/master/inst/paper/Sparks_et_al-main_text.html).

### Compendium DOI:

http://dx.doi.org/xxxxxxx

The files at the URL above will generate the results as found in the publication. The files hosted at https://github.com/openplantpathology/Reproducibility_in_Plant_Pathology are the development versions and may have changed since the report was published.

### Authors of this repository:

Adam H Sparks (<adamhsparks@gmail.com>)

Emerson M Del Ponte (<delponte@ufv.br>)

Sydney Everhart (<everhart@unl.edu>)

Zachary Foster (<zacharyfoster1989@gmail.com>)

Niklaus J Grünwald (<grunwaln@science.oregonstate.edu>)

### Published in:

### Overview of contents

This repository is our research compendium that details our methodology for
examining the state of reproducible research in plant pathology. The compendium
contains all data, code, and text associated with the publication XXXX published
in XXX. The `R markdown format` (`Rmd`) files in the `inst/paper/` directory
contain details of how all the analyses reported in the paper were conducted.
Detailed instructions on methods used and how to rerun the analysis to reproduce
the results are found in the vignettes, in the `vingettes/` directory.

### The supplementary files

The `inst/` directory contains:

- the manuscript as submitted (in MS Word format) and its `Rmd` source file (in
the `paper/` directory)

- supplementary information source files (in `Rmd` format) and executed versions

- all the figures that are included in the paper (in the `figures/` directory)

### The R package

@@

To download the package source as you see it on GitHub, for offline browsing,
use this line at the shell prompt (assuming you have Git installed on your
computer):

```
git clone https://github.com/openplantpathology/Reproducibility_in_Plant_Pathology.git
```

@@

### The Docker image

@@

@@

Manuscript: [CC-BY-4.0](http://creativecommons.org/licenses/by/4.0/)

Code: [MIT](http://opensource.org/licenses/MIT) year: `r format(Sys.Date(),
"%Y")`, copyright holder: Adam H Sparks

Data: [CC-0](http://creativecommons.org/publicdomain/zero/1.0/) attribution
requested in reuse

### Dependencies

We used [RStudio](http://www.rstudio.com/products/rstudio/) on macOS and Ubuntu
16.04 LTS.

We also used [JabRef](http://www.jabref.org/) and 
[Google Sheets](https://www.google.com/sheets/about/).

### Contact

Adam H Sparks, Associate Professor, Centre for Crop Health
University of Southern Queensland
Toowoomba, Queensland 4350

(+61) (7) 4831 1948   e. adam.sparks@usq.edu.au
https://staffprofile.usq.edu.au/Profile/Adam-Sparks

### Credits
This research compendium was based on
https://github.com/benmarwick/researchcompendium but not forked from because it
was already under development when I found Ben's.

>>>>

---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-"
)
```

# Reproducibility.in.Plant.Pathology

[![Travis-CI Build Status](https://travis-ci.org/openplantpathology/Reproducibility_in_Plant_Pathology.svg?branch=master)](https://travis-ci.org/openplantpathology/Reproducibility_in_Plant_Pathology) 
[![DOI](https://zenodo.org/badge/62676177.svg)](https://zenodo.org/badge/latestdoi/62676177)

This repository contains the data and code for our paper:

> Sparks, A.H., Del Ponte, E.M., Everhart, S., Foster, Z., Grünwald, N. (YYYY). _Title of paper_. Name of journal/book <https://doi.org/xxx/xxx>

Our pre-print is online here:

> Authors, (YYYY). _Title of paper_. Name of journal/book, Accessed `r format(Sys.Date(), "%d %b %Y")`. Online at <https://doi.org/xxx/xxx>

### How to cite

Please cite this compendium as:

> Authors, (`r format(Sys.Date(), "%Y")`). _Compendium of R code and data for 'Status and Best Practices for Reproducible Research In Plant Pathology'_. Accessed `r format(Sys.Date(), "%d %b %Y")`. Online at <https://doi.org/10.5281/zenodo.1250665>

### How to download or install

#### The R package

@@

You can download the compendium as a zip from from this URL: <https://github.com/openplantpathology/Reproducibility_in_Plant_Pathology/archive/master.zip>

Or you can install this compendium as an R package, Reproducibility.in.Plant.Pathology, from GitHub with:
```{r gh-installation, eval = FALSE}
# install.packages("devtools")
devtools::install_github("adamhsparks/Reproducibility_in_Plant_Pathology")
```

@@

#### The Docker image

@@

## Meta

@@

**Text and figures :**  [CC-BY-4.0](http://creativecommons.org/licenses/by/4.0/)

**Code :** See the [DESCRIPTION](DESCRIPTION) file

**Data :** [CC-0](http://creativecommons.org/publicdomain/zero/1.0/) attribution requested in reuse

### Contributions

We welcome contributions from everyone. Before you get started, please see our [contributor guidelines](CONTRIBUTING.md). Please note that this project is released with a [Contributor Code of Conduct](CONDUCT.md). By participating in this project you agree to abide by its terms.
